sensitivity_tests_march2025_tables_profit

### 2025-07-31 Code/Paper_analysisandtables.Rmd
Final cleaning (minus figure folder)

#correct data types, levels and reference factors
Data[,c(1:11,16, 19:44, 46:61)] <- lapply(Data[,c(1:11,16, 19:44, 46:61)], factor)
levels(Data$WQ_combined_count) <- c(levels(Data$WQ_combined_count), "4")

@@

Data$HISTORY_OF_E_COLI_PRESENCE_RISK_LEVEL <- relevel(Data$HISTORY_OF_E_COLI_PRESENCE_RISK_LEVEL, ref = "NONE")
Data$TREATMENT_TECHNIUQE_VIOLATIONS_RISK_LEVEL <- relevel(Data$TREATMENT_TECHNIUQE_VIOLATIONS_RISK_LEVEL, ref = "NONE")
Data$PERCENTAGE_OF_SOURCES_EXCEEDING_AN_MCL_RISK_LEVEL <- relevel(Data$PERCENTAGE_OF_SOURCES_EXCEEDING_AN_MCL_RISK_LEVEL, ref = "NONE")
Data$CONSTITUENTS_OF_EMERGING_CONCERN_RISK_LEVEL_BI <- relevel(Data$CONSTITUENTS_OF_EMERGING_CONCERN_RISK_LEVEL_BI, ref = "NONE")
Data$NUMBER_OF_WATER_SOURCES_RISK_LEVEL_BI <- relevel(Data$NUMBER_OF_WATER_SOURCES_RISK_LEVEL_BI, ref = "NONE")
Data$ABESENCE_OF_INTERTIES_RISK_LEVEL <- relevel(Data$ABESENCE_OF_INTERTIES_RISK_LEVEL, ref = "NONE")
Data$BOTTLED_WATER_OR_HAULED_WATER_RELIANCE_RISK_LEVEL <- relevel(Data$BOTTLED_WATER_OR_HAULED_WATER_RELIANCE_RISK_LEVEL, ref = "NONE")
Data$SOURCE_CAPACITY_VIOLATION_RISK_LEVEL <- relevel(Data$SOURCE_CAPACITY_VIOLATION_RISK_LEVEL, ref = "NONE")
Data$PERCENT_OF_MEDIAN_HOUSEHOLD_INCOME_MHI_RISK_LEVEL_BI <- relevel(Data$PERCENT_OF_MEDIAN_HOUSEHOLD_INCOME_MHI_RISK_LEVEL_BI, ref = "NONE")
Data$EXTREME_WATER_BILL_RISK_LEVEL_BI <- relevel(Data$EXTREME_WATER_BILL_RISK_LEVEL_BI, ref = "NONE")
Data$FUNDING_any_failingoratriskonly <- relevel(Data$FUNDING_any_failingoratriskonly, ref = "No")
Data$OPERATOR_CERTIFICATION_VIOLATIONS_RISK_LEVEL <- relevel(Data$OPERATOR_CERTIFICATION_VIOLATIONS_RISK_LEVEL, ref = "NONE")
Data$MONITORING_AND_REPORTING_VIOLATIONS_RISK_LEVEL <- relevel(Data$MONITORING_AND_REPORTING_VIOLATIONS_RISK_LEVEL, ref = "NONE")
Data$DAYS_CASH_ON_HAND_RISK_LEVEL <- relevel(Data$DAYS_CASH_ON_HAND_RISK_LEVEL, ref = "NONE")
Data$OPERATING_RATIO_RISK_LEVEL <- relevel(Data$OPERATING_RATIO_RISK_LEVEL, ref = "NONE")

@@

#MODELS

#Water quality
WQ1 <- glm(WQ_combined_any ~ enfranchisement_final + LN_POP + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(WQ1)

##WQ sub components
ecoli <- glm(HISTORY_OF_E_COLI_PRESENCE_RISK_LEVEL ~ enfranchisement_final + LN_POP + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(ecoli)

TT <- glm(TREATMENT_TECHNIUQE_VIOLATIONS_RISK_LEVEL ~ enfranchisement_final + LN_POP + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(TT)

MCL <- glm(PERCENTAGE_OF_SOURCES_EXCEEDING_AN_MCL_RISK_LEVEL ~ enfranchisement_final + LN_POP + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(MCL)

#Affordability 
Affordability1 <- glm(Affordability_combined_any ~ enfranchisement_final + LN_POP + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Affordability1)

## Affordability sub components
MHI <- glm(PERCENT_OF_MEDIAN_HOUSEHOLD_INCOME_MHI_RISK_LEVEL_BI ~ enfranchisement_final + LN_POP + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(MHI)

extreme <- glm(EXTREME_WATER_BILL_RISK_LEVEL_BI ~ enfranchisement_final + LN_POP + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(extreme)

covid <- glm(didnotapplycovid ~ enfranchisement_final + LN_POP + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(covid)

# TMF
TMF1 <- glm(TMF_combined_any ~ enfranchisement_final + LN_POP + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(TMF1)

## TMF sub components
Opcert_violations <- glm(OPERATOR_CERTIFICATION_VIOLATIONS_RISK_LEVEL ~ enfranchisement_final + LN_POP + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Opcert_violations)

mrviolations <- glm(MONITORING_AND_REPORTING_VIOLATIONS_RISK_LEVEL ~ enfranchisement_final + LN_POP + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(mrviolations)

cash <- glm(DAYS_CASH_ON_HAND_RISK_LEVEL ~ enfranchisement_final + LN_POP + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(cash)

@@

TMF1OR <- TMF1
TMF1OR$coefficients <- exp(TMF1OR$coefficients)
pvaluesTMF1 <- list(summary(TMF1)$coefficients[,4])

@@

compositemodellist <- list(WQ1, WQ1OR, Affordability1, Affordability1OR,
                          TMF1, TMF1OR)

Compositestable <- capture.output(stargazer(compositemodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Water quality", "Affordability", 
                                                    "TMF capacity"), 
                                 ci=c(F,T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(p.valuesWQ1, p.values2, pvaluesAffordability1, p.values2,
                                       pvaluesTMF1, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Limited enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                apply.ci = function(x) { 0 }))

@@

WQtable <- capture.output(stargazer(WQmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("E. coli", "Treatment technique violations", "MCL violations"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesecoli, p.values2, pvaluesTT, p.values2,
                                       pvaluesMCL, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Limited enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

AFtable <- capture.output(stargazer(AFmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Unaffordable bill", "Extreme bill",
                                                    "No arrearage relief"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesMHI, p.values2, pvaluesextreme, p.values2, pvaluescovid, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Limited enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

```{r table TMF, results='asis', echo=FALSE}
#TMF indicators
Opcert_violationsOR <- Opcert_violations
Opcert_violationsOR$coefficients <- exp(Opcert_violationsOR$coefficients)
pvaluesOpcert <- list(summary(Opcert_violations)$coefficients[,4])

mrviolationsOR <- mrviolations
mrviolationsOR$coefficients <- exp(mrviolationsOR$coefficients)
pvaluesmrviolations <- list(summary(mrviolations)$coefficients[,4])

cashOR <- cash
cashOR$coefficients <- exp(cashOR$coefficients)
pvaluescash <- list(summary(cash)$coefficients[,4])

TMFmodellist <- list(Opcert_violations, Opcert_violationsOR, mrviolations, mrviolationsOR, cash, cashOR)

TMFtable <- capture.output(stargazer(TMFmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Operator cert. violations", "M&R violations", "Cash on hand"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesOpcert, p.values2, pvaluesmrviolations, p.values2, pvaluescash, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Limited enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

cat(paste(gsub("\\(0.000, 0.000\\)", "", TMFtable), collapse = "\n"), "\n")
```

@@

```{r descriptives for demofraphics, results='asis', echo=FALSE}
Data_mini <- Data %>% select(enfranchisement_final, MHI, LN_POP, Source, Percent.renter, Percent.white, POPULATION, CALENVIRO_SCREEN_SCORE, FAILING, WQ_combined_any, Affordability_combined_any, TMF_combined_any, Accessibility_combined_any, Percent.hispanicorlatino, Percent.black, Percent.asian)

>>>>

#correct data types, levels and reference factors
Data[,c(1:11,16, 19:45, 47:61)] <- lapply(Data[,c(1:11,16, 19:45, 47:61)], factor)
levels(Data$WQ_combined_count) <- c(levels(Data$WQ_combined_count), "4")

@@

Data$HISTORY_OF_E_COLI_PRESENCE_RISK_LEVEL <- relevel(Data$HISTORY_OF_E_COLI_PRESENCE_RISK_LEVEL, ref = "NONE")
Data$TREATMENT_TECHNIUQE_VIOLATIONS_RISK_LEVEL <- relevel(Data$TREATMENT_TECHNIUQE_VIOLATIONS_RISK_LEVEL, ref = "NONE")
Data$PERCENTAGE_OF_SOURCES_EXCEEDING_AN_MCL_RISK_LEVEL <- relevel(Data$PERCENTAGE_OF_SOURCES_EXCEEDING_AN_MCL_RISK_LEVEL, ref = "NONE")
Data$NUMBER_OF_WATER_SOURCES_RISK_LEVEL_BI <- relevel(Data$NUMBER_OF_WATER_SOURCES_RISK_LEVEL_BI, ref = "NONE")
Data$ABESENCE_OF_INTERTIES_RISK_LEVEL <- relevel(Data$ABESENCE_OF_INTERTIES_RISK_LEVEL, ref = "NONE")
Data$BOTTLED_WATER_OR_HAULED_WATER_RELIANCE_RISK_LEVEL <- relevel(Data$BOTTLED_WATER_OR_HAULED_WATER_RELIANCE_RISK_LEVEL, ref = "NONE")
Data$SOURCE_CAPACITY_VIOLATION_RISK_LEVEL <- relevel(Data$SOURCE_CAPACITY_VIOLATION_RISK_LEVEL, ref = "NONE")
Data$PERCENT_OF_MEDIAN_HOUSEHOLD_INCOME_MHI_RISK_LEVEL_BI <- relevel(Data$PERCENT_OF_MEDIAN_HOUSEHOLD_INCOME_MHI_RISK_LEVEL_BI, ref = "2")
Data$EXTREME_WATER_BILL_RISK_LEVEL_BI <- relevel(Data$EXTREME_WATER_BILL_RISK_LEVEL_BI, ref = "2")
Data$FUNDING_any_failingoratriskonly <- relevel(Data$FUNDING_any_failingoratriskonly, ref = "No")
Data$OPERATOR_CERTIFICATION_VIOLATIONS_RISK_LEVEL <- relevel(Data$OPERATOR_CERTIFICATION_VIOLATIONS_RISK_LEVEL, ref = "NONE")
Data$MONITORING_AND_REPORTING_VIOLATIONS_RISK_LEVEL <- relevel(Data$MONITORING_AND_REPORTING_VIOLATIONS_RISK_LEVEL, ref = "NONE")
Data$DAYS_CASH_ON_HAND_RISK_LEVEL <- relevel(Data$DAYS_CASH_ON_HAND_RISK_LEVEL, ref = "NONE")
Data$OPERATING_RATIO_RISK_LEVEL <- relevel(Data$OPERATING_RATIO_RISK_LEVEL, ref = "NONE")

@@

#Water quality
WQ1 <- glm(WQ_combined_any ~ enfranchisement_final + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(WQ1)

##WQ sub components
ecoli <- glm(HISTORY_OF_E_COLI_PRESENCE_RISK_LEVEL ~ enfranchisement_final + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(ecoli)

TT <- glm(TREATMENT_TECHNIUQE_VIOLATIONS_RISK_LEVEL ~ enfranchisement_final + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(TT)

MCL <- glm(PERCENTAGE_OF_SOURCES_EXCEEDING_AN_MCL_RISK_LEVEL ~ enfranchisement_final + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(MCL)

#Affordability 
Affordability1 <- glm(Affordability_combined_any ~ enfranchisement_final + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Affordability1)

## Affordability sub components
MHI <- glm(PERCENT_OF_MEDIAN_HOUSEHOLD_INCOME_MHI_RISK_LEVEL_BI ~ enfranchisement_final + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(MHI)

extreme <- glm(EXTREME_WATER_BILL_RISK_LEVEL_BI ~ enfranchisement_final + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(extreme)

covid <- glm(didnotapplycovid ~ enfranchisement_final + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(covid)

# Accessibility
Accessibility1 <- glm(Accessibility_combined_any ~ enfranchisement_final + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Accessibility1)

## Accessibility sub components
Single_source <- glm(NUMBER_OF_WATER_SOURCES_RISK_LEVEL_BI ~ enfranchisement_final + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Single_source)

Sourcecapacity_violations <- glm(SOURCE_CAPACITY_VIOLATION_RISK_LEVEL ~ enfranchisement_final + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Sourcecapacity_violations)

Service_dis <- glm(Service_disruptions ~ enfranchisement_final + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Service_dis)

@@

Accessibility1OR <- Accessibility1
Accessibility1OR$coefficients <- exp(Accessibility1OR$coefficients)
pvaluesAccessibility1 <- list(summary(Accessibility1)$coefficients[,4])

@@

compositemodellist <- list(WQ1, WQ1OR, Affordability1, Affordability1OR,
                          Accessibility1, Accessibility1OR)

Compositestable <- capture.output(stargazer(compositemodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Water quality", "Affordability", 
                                                    "Accessibility"), 
                                 ci=c(F,T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(p.valuesWQ1, p.values2, pvaluesAffordability1, p.values2,
                                       pvaluesAccessibility1, p.values2),
                                 omit.stat = c("ll"),
                                 covariate.labels = c("Limited enfran.", "No enfran.",
                                                      "Population", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                apply.ci = function(x) { 0 }))

@@

WQtable <- capture.output(stargazer(WQmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("E. coli", "Treatment technique violations", "MCL violations"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesecoli, p.values2, pvaluesTT, p.values2,
                                       pvaluesMCL, p.values2),
                                 omit.stat = c("ll"),
                                 covariate.labels = c("Limited enfran.", "No enfran.",
                                                      "Population", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

AFtable <- capture.output(stargazer(AFmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Unaffordable bill", "Extreme bill",
                                                    "No arrearage relief"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesMHI, p.values2, pvaluesextreme, p.values2, pvaluescovid, p.values2),
                                 omit.stat = c("ll"),
                                 covariate.labels = c("Limited enfran.", "No enfran.",
                                                      "Population", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

```{r table Accessibility, results='asis', echo=FALSE}
#Accessibility indicators
Single_sourceOR <- Single_source
Single_sourceOR$coefficients <- exp(Single_sourceOR$coefficients)
pvaluesSinglesource <- list(summary(Single_source)$coefficients[,4])

Sourcecapacity_violationsOR <- Sourcecapacity_violations
Sourcecapacity_violationsOR$coefficients <- exp(Sourcecapacity_violationsOR$coefficients)
pvaluesSourcecapacity_violations <- list(summary(Sourcecapacity_violations)$coefficients[,4])

Service_disOR <- Service_dis
Service_disOR$coefficients <- exp(Service_disOR$coefficients)
pvaluesService_dis <- list(summary(Service_dis)$coefficients[,4])

Accessmodellist <- list(Single_source, Single_sourceOR, Sourcecapacity_violations, Sourcecapacity_violationsOR, Service_dis, Service_disOR)

Accesstable <- capture.output(stargazer(Accessmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Single source", "Source capacity violations", "Service disruptions"), 
                                 ci=c(F,T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesSinglesource, p.values2, pvaluesSourcecapacity_violations, p.values2, pvaluesService_dis, p.values2),
                                 omit.stat = c("ll"),
                                 covariate.labels = c("Limited enfran.", "No enfran.",
                                                      "Population", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

cat(paste(gsub("\\(0.000, 0.000\\)", "", Accesstable), collapse = "\n"), "\n")
```

@@

```{r descriptives for demofraphics, results='asis', echo=FALSE}

Data_mini <- Data %>% select(enfranchisement_final, MHI, LN_POP, Source, Percent.renter, Percent.white, POPULATION, CALENVIRO_SCREEN_SCORE, FAILING, WQ_combined_any, Affordability_combined_any, Accessibility_combined_any, Percent.hispanicorlatino, Percent.black, Percent.asian, Source_bi)

### 2025-07-31 Code/sensitivity_tests_march2025_tables_profit.Rmd
Final cleaning (minus figure folder)

#LOAD AND READY DATA
Data <- read.csv(here::here("Data_processed/Systemperformancedata_RR.csv"))
Data <- Data[,-1]
Data$enfranchisement_final <- as.factor(Data$enfranchisement_final)
Data$Final_inst_update <- as.factor(Data$Final_inst_update)

>>>>

#LOAD AND READY DATA
Data <- read.csv(here::here("Data_processed/Systemperformancedata.csv"))
Data <- Data[,-1]
Data$enfranchisement_final <- as.factor(Data$enfranchisement_final)
Data$Final_inst_update <- as.factor(Data$Final_inst_update)
